Malacology: A Programmable Storage System

### 2016-10-11 paper/paper.tex

\begin{table*}
\centering
\begin{tabular}{  l | l | l | l | l}
\textbf{Interface}            &
\textbf{\text{*}}             &
\textbf{Provides...}          &
\textbf{Example in Storage} & \\ \hline
Load Balancing  & migration \& monitoring primitives   & \\
Versioning      & consistency primitives               & \\ 
Shared Resource & serialization \& batching primitives
                & \\
Durability      & persistence primitives
                & \\
Logical Device  & transaction \& atomicity primitives 
                & Swift/ZeroVM in situ storage \& compute [1] \\ 
\end{tabular}
\caption{The Malacology interfaces are commonly used abstractions used
internally in storage stacks.}
\label{table:implementation}
\end{table*}
% http://www.zerovm.org/zerocloud.html

@@

\label{services}
\begin{table}
\centering
\begin{tabular}{  l | l | l | l}
\textbf{Service}              &
\textbf{Used to...}           &
\textbf{Malacology Interface} & \\ \hline
Mantle & load balance metadata     & Load Balancing  \\
       & agree on current balancer & Versioning      \\ 
       & control client write lock & Shared Resource \\
       & persist policy logic      & Durability      \\ \hline
ZLog   & implement CORFU           & Logical Device  \\ 
       & install ZLog interfaces   & Versioning      \\
       & persist log entries       & Durability      \\ \hline
ZLog   & load balance sequencers   & Load Balancing  \\
Seqr.  & guard shared resource     & Shared Resource \\ 
\end{tabular}
\caption{Mantle and ZLog are built using Malacology interfaces so they inherit the
robustness of the subsystems of the underlying stack. The \cmark s are
interfaces contributed in this paper; durability is already provided with a
client library and the MDS Logical Device is already
published~\cite{sevilla:sc15-mantle}. }
\label{table:implementation}
\end{table}

>>>>

\begin{table*}
\centering
\title{Hi}
\begin{tabular}{  l | l | l | l }
\multicolumn{4}{c}{\Large \textbf{Common Internal Abstractions}} \\
\multicolumn{4}{c}{} \\
\textbf{Abstraction}                    &
\textbf{Example in Production Systems}  &
\textbf{Example in Ceph}                &
\textbf{Provided Primitives}            \\ \hline
{\it Versioning}
  & Zookeeper coordination~\cite{hunt_zookeeper_2010}, Chubby~\cite{website:chubby}
  & cluster state management~\cite{website:ceph-mon}
  & consensus \& consistency
  \\
{\it Shared Resource}
  & MPI collective IO, burst
  & POSIX metadata protocols
  & serialization \& batching
  \\
{\it Logical Device}
  & Swift in situ storage/compute~\cite{website:zerocloud}
  & object interface classes~\cite{website:cls-lua}
  & transaction \& atomicity
  \\
Durability
  & S3/Swift interfaces (RESTful API)
  & object store library~\cite{weil_rados_2007}
  & interface to persistence
  \\
Load Balancing
  & VMWare's VM migration~\cite{vmware-drs,gulati:hotcloud2011-cloud-resource-management} 
  & migration in metadata cluster~\cite{weil:sc2004-dyn-metadata}
  & migration \& monitoring
  \\
\end{tabular}
\caption{The same ``internal abstractions" are common across large-scale
systems because they provide primitives that solve general distributed systems
problems.  Here we list examples of what these internal abstractions are used
for in ``production systems" and in Ceph.  Malacology provides these internal
abstractions as interfaces that higher level applications can use; {\it
italicized abstractions} are interfaces contributed in this paper.}
\label{table:examples}
\end{table*}

@@

\label{services}
\begin{table}
\centering
\begin{tabular}{  l | l | l }
\textbf{Service}              &
\textbf{Used to...}           &
\textbf{Malacology Interface} \\ \hline
Mantle & load balance metadata     & Load Balancing  \\
       & agree on current balancer & Versioning      \\ 
       & control client write lock & Shared Resource \\
       & persist policy logic      & Durability      \\ \hline
ZLog   & implement CORFU           & Logical Device  \\ 
       & install ZLog interfaces   & Versioning      \\
       & persist log entries       & Durability      \\ \hline
ZLog   & load balance sequencers   & Load Balancing  \\
Seqr.  & guard shared resource     & Shared Resource \\ 
\end{tabular}
\caption{Mantle and ZLog are built using Malacology interfaces so they inherit the
robustness of the subsystems of the underlying stack.}
\label{table:implementation}
\end{table}
